---
title: "Chapter 12 & 15 Exercise"
output: html_notebook
Name: Daniel Lee
---

### Problem 12.1 
```{r}
BabyNames %>%
  group_by(sex, name) %>%
  summarise(count = sum(count)) %>%
  mutate(popularity = rank(desc(count))) %>%
  filter(popularity <= 5)
```

### Problem 12.2
```{r}

PopularCounts <-
  BabyNames %>%
  group_by(year, name) %>%
  summarise(total = sum(count)) %>%
  mutate(ranking = ifelse(rank(desc(total)) <= 100, "Top_100", "Below")) %>%
  group_by(year, ranking) %>%
  summarise(total = sum(total))

GlyphReady <-
  PopularCounts %>%
  spread(ranking, total) %>%
  mutate(frac_in_top_100 = Top_100 / (Top_100 + Below))

GlyphReady %>%
  ggplot(aes(x=year, y=frac_in_top_100)) + 
  geom_line() + 
  ylim(0, NA)
```

### Problem 12.3

a. Summary function
b. neither a summary n or a transformation. It is a pair of values rather than a single value as required for a summary function
c. Summary function
d. transformation function
e. transformation function 
f. summary function
g. transformation function
h. summary function: an entire set of dates is being truned into a single number. 


### Problem 15.1 
1.
```{r}
lubridate::mdy("April 30, 1777") - lubridate::mdy("February 26, 1999")
```
2. 
```{r}
lubridate::mdy("06-23-1912") - lubridate::mdy("02-26-1999")
```

3. 
```{r}
lubridate::dmy("3 March 1847") - lubridate::dmy("26-02-1999")
```
4. 
```{r}
lubridate::mdy_hm("11:00 am on Nov. 11th, 1918 at 11:00 am") - lubridate::mdy_hm("04:00 am on Feb. 26th, 1999 at 04:00 am")
```
5.
```{r}
lubridate::mdy("July 20, 1969") - lubridate::mdy("February 26, 1999")
```


### Problem 15.2
a.
b.
c.
d.
e.
f.
g.
h.
i.


### Problem 15.3 
```{r}
library(rvest)
library(RCurl)
web_page <-
  "http://en.wikipedia.org/wiki/Mile_run_world_record_progression"

SetOfTables <-
  web_page %>%
  rvest::html() %>%
  readHTMLTable(stringsAsFactors=FALSE)

T4 <- SetOfTables[[4]]

T4 %>%
  mutate(Date = gsub("\\[.\\]$", "", Date)), Time = lubridate::as.duration(ms(Time))/60, Date = dmy(Date)) %>%
  ggplot(aes(x=Date, y=Time)) +
  geom_point() + 
  geom_text(aes(label=Athlete), size=3, angle=45, hjust=-0.1) + 
  ylim(3.5,4.4) + ylab("Time (hours)") +
  xlim(ymd("1910-01-01"), ymd("2021-01-01"))
```


